%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Developer/Assistant Instructor} % Job title
    {Evangadi Bootcamp} % Organization
    {MD, USA} % Location
    {Mar 2020 - Current} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lead student progress, provided instructional materials, and taught courses in HTML, CSS, JavaScript, Node.js, Express, MySQL, MongoDB, React Hooks, Context API, Routing and React.js.}
        \item {Supported students with learning difficulties and assisted in project development.}
        \item {Collaborated with instructors to plan and deliver React.js lessons.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Front End React Developer} % Job title
    {Bitwise Industries} % Organization
    {CA, USA} % Location
    {Jun 2021 - Feb 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and implemented web applications using React, Redux, HTML5, CSS3, and Bootstrap.}
        \item {Utilized Redux thunk for asynchronous actions and axios for AJAX requests.}
        \item {Ensured cross-browser compatibility and performed client-side validations.}
        \item {Collaborated in an Agile environment using JIRA.}
      \end{cvitems}
    }

 %---------------------------------------------------------
  \cventry
    {Full Stack Developer} % Job title
    {Ertale Tech} % Organization
    {MD, USA} % Location
    {Mar 2017 - Feb 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed page layouts, animation, and navigation using HTML5, CSS3, and JavaScript.}
        \item {Implemented Single Page Application routes and handled user data with AJAX and JSON.}
        \item {Collaborated with backend teams in an Agile environment using Git and JIRA.}
      \end{cvitems}
    }

%---------------------------------------------------------   
\end{cventries}
